\def\company{Cedar}
\def\position{Sr. Software Engineer (Communications Platform)}
\relevantskill{HIPAA}{coresystems}
\relevantskill{Across the Stack}{nexus,centralpark,passport,finch,points,homepage,eriemobile,xpay,datacomm}
\relevantskill{Technical Debt}{xpay,nexus,passport}
\relevantskill{Cross-functional Collab}{leandogcollab,nexus,coresystems,cronosysprojects,finch,points}
\relevantskill{System Design}{centralpark,points,passport,cronosysprojects}
\relevantskill{Communication}{guided,whitepaper,cronosysprojects}
\def\coverbody{
   Hello!

   Usually I write something here about how I match technically, but this time I want
   to tell a story:

   My ex-wife had some chronic medical issues, and I had medical insurance.  In spite of
   that, for many years I had a stack of bills about an inch thick.  I worked toward
   paying them all off--and eventually did--but for a very, very long time my credit was
   terrible, and each pay period, I would receive new bills.

   It took several hours each paycheck, but I would sort the bills by amount, put the
   newer bill into the stack, find out if there was an older duplicate, throw that one
   away.  Sometimes, the bill would move from one company to another company--sometimes
   between debt collectors, but sometimes even before going to collections there were
   duplicate bills for the same services on different letterhead.

   The bills that would go to collections would sometimes be consolodated into one
   statement, so I had to figure out which line items--often printed in light grey on the
   back--lined up with which bills already in the pile.  In spite of all this, I'm sure
   I've double-paid bills.  I've definitely discovered duplicates well after the fact.
   (You can add to this the bills that I either plain lost or never received, which I had to
   comb through my credit report to find and pay.)

   At this point, I paid them, from smallest to largest to try to reduce the number of
   marks on my credit as much as possible.

   It was absolutely grueling and a sad indictment of how medical care works in this
   country.

   I would love the opportunity to discuss this role.
}
