%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Letter of Notice
% LaTeX Template
% Version 1.1 (21/11/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rashadul Islam (ross08@gmail.com) with modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % 11pt default font size, other options: 12pt and 10pt

\usepackage[a4paper, top=2cm]{geometry} % Use A4 paper size

\usepackage{xcolor} % Required for color customization

%\usepackage{fouriernc} % Use the New Century Schoolbook font, comment this line to use the default LaTeX font or replace it with another
\usepackage[sfdefault]{FiraSans} % Change this to use any font, but keep it simple

\definecolor{cvblue}{HTML}{304263} % Define a custom color for the heading box

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	DATE AND FROM ADDRESS
%----------------------------------------------------------------------------------------

\date{\vspace{1.5cm}\begin{flushleft}\today\end{flushleft}} % Use todays date and left-align it

\begin{letter}{\large \bfseries Centegix} % From address or department

%----------------------------------------------------------------------------------------
%	HEADING BOX
%----------------------------------------------------------------------------------------

\colorbox{cvblue!90}{ % Creates a highlight behind the text using the previously-defined navy color

\parbox[t]{\linewidth}{ % Creates a box to take up the entire line width

\vspace*{14pt} % Whitespace above the text

\hfill \color{white} \textsc{\huge Staff Engineer, Golang/Backend} % Right-aligned heading text

\vspace*{14pt} % Whitespace below the text
}}

%----------------------------------------------------------------------------------------
%	SIGNATURE
%----------------------------------------------------------------------------------------

\signature{
Jason Felice \\ % Your name
\small{E: jason.m.felice@gmail.com\\ M: +1-216-466-4122} % Contact information
}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Centegix,}

{\bf TL;DR} I am a cross-stack, hands-on, top-tier engineer (as well as an actual human
being and not a robot) and I'd love a chance to help improve this tech org.

I meet all the requirements you mention:

\begin{itemize}
\item Expert-level at Go, have used GCP, have extensively used AWS.
\item I've given talks on unit testing, but also bring it in to every project that didn't already have it and improve it where it's been.
\item Have spent tons of time implementing DevOps enablement systems and processes.
\item Have designed and implemented dozens of APIs.
\item Have very strong communication skills, especially written.
\item Have continually learned.
\item Have been in the Agile community for ages, and have applied and advocated for concepts regularly.
\item And finally, I always learn almost the entire stack, whether at Groupon or 2U, in order to deliver projects.
\end{itemize}

My biggest value, though, is my breadth.  I have been on so many projects with so many different tech stacks,
that I have the ability to point out what makes things simpler, why something will or will not fail, or
whether some particular project design will result in the project becoming stuck in a never-ending maintenance quagmire.

I almost always become the go-to person for architecture, I mentor junior and mid-level engineers through
a combination of processes, from pair programming and code review, through advocating for special-interest
groups.

And I often advocate for organizational change when I see opportunity to improve the tech org or
the company as a whole.


\closing{Sincerely,}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
