\def\company{Clover}
\def\position{Senior Software Engineer}
\relevantskill{Python}{xpay,coresystems}
\relevantskill{Ruby}{cronosysprojects}
\relevantskill{C and C++}{cronosysprojects,xpay,kak-ansi,gambit-objc,rep,eriemobile}
\relevantskill{Java}{cronosysprojects,eriemobile,xpay}
\relevantskill{System Design}{points,auth21,webtech,homepage,nexus,centralpark}
\relevantskill{Mentoring}{cronosysprojects,points,centralpark,xpay,coresystems}
\relevantskill{Scalable+Distributed}{nexus,points,passport}
\relevantskill{Soup to Nuts}{webtech,points,centralpark}
\def\coverbody{
   Hello!

   I am a top-level engineer with broad experience who has built many scalable
   systems.  I'm fluent in perhaps a dozen languages, including all the ones
   on your list (although my Python might need a bit of work these days).

   As a tech lead, which I've been on most of my projects for about 11 years
   now, I'm definitely comfortable working across different tech stacks,
   collaborating with other teams, making it easier for them to do what
   we need to deliver or doing it ourselves when possible.

   On refactoring complex (often distributed) systems, this is practically
   my claim to fame.  At Groupon, during one of our infamous hackathons, I
   chose to use automated methods to detect and remove dead code from the
   primary Ruby on Rails codebase, and ended up removing several thousands
   of lines.  This was a large codebase that had about 300 daily committers.

   Building systems that support people's health sounds interesting, and I'd
   love to talk to you about it.
}
