\def\company{Command|Link}
\dev\position{}
\relevantskill{Go}{nexus,coresystems}
\relevantskill{PHP}{cronosysprojects,webtech}
\relevantskill{Python}{xpay,coresystems}
\relevantskill{Locks+CAS+nonblocking IO}{centralpark,auth21,xpay,nexus,passport}
\relevantskill{Kafka+RabbitMQ+NATS}{points,homepage,finch,passport}
\relevantskill{Reactive+Back-pressure}{nexus,points,homepage,passport,xpay}
\relevantskill{OAuth}{nexus,centralpark,coresystems}
\relevantskill{HMAC+mTLS+secrets}{auth21,xpay,nexus}
\def\coverbody{
   I'm a Principal Engineer with deep experience in most of the low-level concepts you've put in your posting:

   \begin{itemize}
   \item I was deep in the weeds with threading and concurrency primitives for the one credit authorization system that I wrote (Auth21) and the two others I maintained.
   \item Those same systems required a lot of work with cryptography, HMAC, mTLS, and secrets.
   \item I used Kafka and RabbitMQ heavily at Groupon for the Points project.  These were idempotent, durable flows.  I've also used Kenesis, SNS/SQS, NATS, and probably others.
   \item I've played with Akka, but I've used Go's built-in actors, Clojure's agent and core.async, Erlang and Elixir's implementation of CSP, etc.
   \item OAuth 2.0 was a significant part of the systems that I pushed to unify at 2U.
   \end{itemize}

   As a Principal Engineer, I don't just code (though I do mostly code), but I pair, mentor juniors and mid-level engineers,
   advocate for organizational support, and propose, facilitate and contribute to architectural decisions.

   I'd love a chance to talk about this position!
}
% SD-WAN Product of the Year
% SaaS Product of the Year
% 
% ITSM Visionary Spotlight - Overall Visionary Spotlight, for ITSM Platform.
% UCaaS Product of the Year
