%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Letter of Notice
% LaTeX Template
% Version 1.1 (21/11/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rashadul Islam (ross08@gmail.com) with modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % 11pt default font size, other options: 12pt and 10pt

\usepackage[a4paper, top=2cm]{geometry} % Use A4 paper size

\usepackage{xcolor} % Required for color customization

%\usepackage{fouriernc} % Use the New Century Schoolbook font, comment this line to use the default LaTeX font or replace it with another
\usepackage[sfdefault]{FiraSans} % Change this to use any font, but keep it simple

\definecolor{cvblue}{HTML}{304263} % Define a custom color for the heading box

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	DATE AND FROM ADDRESS
%----------------------------------------------------------------------------------------

\date{\vspace{1.5cm}\begin{flushleft}\today\end{flushleft}} % Use todays date and left-align it

\begin{letter}{\large \bfseries Domino Data Lab} % From address or department

%----------------------------------------------------------------------------------------
%	HEADING BOX
%----------------------------------------------------------------------------------------

\colorbox{cvblue!90}{ % Creates a highlight behind the text using the previously-defined navy color

\parbox[t]{\linewidth}{ % Creates a box to take up the entire line width

\vspace*{14pt} % Whitespace above the text

\hfill \color{white} \textsc{\huge Senior/Staff Engineer, Compute} % Right-aligned heading text

\vspace*{14pt} % Whitespace below the text
}}

%----------------------------------------------------------------------------------------
%	SIGNATURE
%----------------------------------------------------------------------------------------

\signature{
Jason Felice \\ % Your name
\small{E: jason.m.felice@gmail.com\\ M: +1-216-466-4122} % Contact information
}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Domino,}

{\bf TL;DR} I'm qualified for and excited about this position, and am also absolutley a real
human being directly typing these symbols into my computer for you to read, dear hiring manager.

I'm a hands-on engineer with a broad familiarity with many modern languages, including most
of the ones in your post: Expert level at C++, Java, and Go, and familiar with Scala and Kotlin
(but not C\#).

I bring very good algorithm and data structure knowledge, and am truly exceptional at
the optimization of existing processes, reducing resources and improving runtimes.  The
TopCoder link in my resume will show you how I performed on what are now called "Data Science
Matches" -- competitions to produce better answers to computationally intensive problems
with limited CPU and memory.  Examples of applying this for real production code
are highlighted on my resume under the "Algorithms" and "Data Structures" bullets.

At Groupon, I developed large distributed systems that had to perform under the dreaded
"Starbucks Deal" -- the highest-traffic times site, preceeded by much vetting and load
testing.  My systems - 1. a points-based customer retention program and 2. the front page
of the groupon.com website -  worked without issue.

Finally, I've been at the top of the tech ladder for nine years.  I will always be hands-on
coding, but I also mentor engineers and shape the organizations that I work in so that we
make better products.

This position seems right up my alley, and I'm excited about the opportunity to contribute
to something that I can believe in!

\closing{Sincerely,}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
