\def\company{Gusto}
\def\position{Software Engineer, Async Team}
\relevantskill{Ruby on Rails}{homepage,finch,cronosysprojects}
\relevantskill{Kafka}{points,homepage}
\relevantskill{SNS/SQS}{nexus,coresystems,centralpark}
\relevantskill{Asynchronous Processing}{nexus,passport,centralpark,xpay}
\relevantskill{Developer Tooling}{nexus,xpay,mobilecicd}
\relevantskill{Infra. Enhancement}{guided,whitepaper,nexus}
\def\coverbody{
   Hello!

   While I'm not versed in Sidekiq, I have a lot of experience with Kafka,
   RabbitMQ, SNS/SQS, NATS, as well a few terrible home-grown solutions
   (a few in-memory in C++, and one in a PostgreSQL table).  I mention the
   last ones because troubleshooting the problems caused by these involved
   some deep dives on how deadlocks and races, multiple-deliveries, and
   visibility timeouts should and should not work.

   My last role was SRE/DevOps-adjacent as I built out the developer
   tooling and infrastructure for CI/CD, encrypted in-repo secrets
   management, as well as secret validation and injection and scaling.
   "Adjacent" in this context means, "I'm not the person who can install
   or manage a Kubernetes cluster, but I know how it works and can write
   helm charts, CI/CD pipelines, edit existing helm charts managed by SRE,
   evaluate and deploy Dapr to Kubernetes for use by other teams."  Primarily,
   I write code--but I do know enough about infrastructure to do those
   things.

   My Ruby on Rails experience dates back to 2005ish, for small projects
   back then.  Skip forward to Blue Frog Gaming for a little bit of work,
   then forward some more for Groupon's PWA with 300 daily committers,
   where I shipped features (and also won an award for using the hack
   week to delete thousands of lines of dead code).

   I'd love a chance to talk aobut this position!
}

