\def\company{Human Interest}
\def\position{Senior Software Engineer, Builder Tools}
\relevantskill{AWS/GCP}{nexus,centralpark,guided,passport,coresystems}
\relevantskill{Terraform/IaC/CF}{nexus,centralpark,coresystems}
\relevantskill{CI/CD Pipelines}{mobilecicd,nexus,points,xpay}
\relevantskill{Communication}{guided,whitepaper}
\relevantskill{Testable Code}{xpay,cronosysprojects,polarpuzzles,eriemobile,finch,points,nexus,passport,centralpark}
\def\coverbody{
   Hello!

   For the last several years, I've been filling a role like the one you describe.
   During my last two roles at 2U, I've been the person to build and fix the tools
   that other developers use to deliver faster and better software--Implementing CI,
   CD, including the necessary architectural changes to code, automating away
   configuration issues with software, making the systems simpler by providing
   services that work across the stack, advocating for a unified authentication
   system to dramatically reduce the work of individual teams, and on and on.

   And historically, this obsession with making the delivery pipeline painless goes
   way back.  On my resume, for DAS I implemented processes dramatically reducing
   delivery failures.  This was above my official role as developer at the time,
   but I noticed some things that told me something was wrong.  We were delivering
   new software to QA very quickly, but we were also fixing things all the time,
   and some of the projects still weren't moving.  Tracking and visualization
   helped uncover that much of the software we delivered had failures that could
   easily be prevented, and automated checking of configs and some process changes
   made delivery failures almost nonexistent after this point.

   I think I could do the world some good in this role, and I'd love the opportunity
   to talk to you about it!
}
