\def\company{Kunai}
\def\position{Lead Software Engineer - Golang}
\relevantskill{Credit+Payment Networks}{auth21,xpay}
\relevantskill{Distributed Systems}{points}
\relevantskill{Microservices}{coresystems,points,homepage,finch}
\relevantskill{Kafka}{points,homepage}
\relevantskill{AWS Services}{centralpark,coresystems,nexus}
\relevantskill{AuroraDB}{passport}
\relevantskill{Golang}{nexus,coresystems}
\relevantskill{Java}{xpay,centralpark,homepage,eriemobile,cronosysprojects}
\relevantskill{Python}{xpay,coresystems}
\def\coverbody{
  I think I have {\bf more} than the qualifications you ask.

  I have six years of experience working directly with payment networks implementing
  and certifying protocols for retail systems - credit, debit, check,
  ACH, private label, etc.  I built one new system from scratch and maintained
  two others, handling everything including network-level, encryption, and parallelization of processing.

  I'm currently expert-level with Go, owing to using it daily for the last five years.
  I count 12 years with microservices, three or
  four with Kafka, nine with AWS, more than 20 with Java, and a couple with Python.

  In my last position (2U), I was very deep into database performance with one of our system's AuroraDB,
  making big changes with a significant benefit.

  At 2U, I built and maintained many serverless solutions, including ones built on AWS Lambda and Step Function.
  While I was not on the DevOps team, I was the go-to developer for doing DevOps work, and the go-to contact
  for DevOps to answer questions about how the system could scale.

  At Groupon, I built high-performance, Kafka-based systems that had to survive load testing
  at 6,000 TPM prior to our dreaded "Starbucks deal" days (ours always did).
}
