\def\company{SentinelOne}
\def\position{Senior Staff Software Engineer}
\relevantskill{\bf Monolith $\rightarrow$ Microservices}{nexus}
\relevantskill{Go}{nexus,coresystems}
\relevantskill{Java}{eriemobile,xpay,cronosysprojects}
\relevantskill{Microservices}{nexus,centralpark,coresystems,points,homepage}
\relevantskill{Distributed Systems}{nexus,centralpark,coresystems,points}
\relevantskill{Modernize Architecture}{nexus,centralpark,guided}
\relevantskill{AWS/GCP}{centralpark,coresystems,passport,nexus}
\relevantskill{Python}{xpay,coresystems}
%\relevantskill{REST APIs}{nexus,coresystems,passport}
%\relevantskill{Agile/XP}{leandogcollab,kanban}
\def\coverbody{
  Hello!

Your "ambitious initiative" to break down a complex monolith into scalable, multi-tenant, cloud-native services matches exactly what I spent three years doing. (See the first bullet on my resume.)

My services lived in a monorepo but shared logic through code and state through a central database in ways that proved difficult to track and modify—creating monolithic properties.

I agree this work is ambitious. I took over after two failed attempts. But it was necessary. Before my work, all five squads coordinated deploys, resulting in massive weekly manual multi-stage deploys that slowed us down and created unnecessary risk and downtime.

I succeeded. Teams now deploy independently. The system gained zero-downtime deploys, healing, and scaling capabilities.

Success required architectural and agile principles, organizational coordination, developer advocacy, making benefits visible, and creating new paths for system modification that aligned developers' easiest path with our goals.

This sounds exciting and well within my expertise. I'd love to discuss this position!
}
