\def\company{SonicWall}
\def\position{Principal API Engineer}
\relevantskill{Go}{nexus,coresystems}
\relevantskill{\bf API Design \& Architecture}{nexus,passport,centralpark,guided}
\relevantskill{Zero Trust \& Security}{nexus,xpay,auth21}
\relevantskill{Cloud-Native/SaaS}{centralpark,coresystems,nexus,passport}
\relevantskill{Technical Leadership}{nexus,guided,whitepaper}
\relevantskill{Mentoring Teams}{leandogcollab,guided,centralpark,nexus}
\relevantskill{CI/CD/CT}{mobilecicd,nexus,xpay}
\relevantskill{DevOps}{points,homepage,nexus,centralpark,passport,guided}
\def\coverbody{
   Hello!

   The role you are describing--tech lead, onshore subject-matter expert,
   mentor, and leader for offshore contractors--is one that I was in for
   three years on a project written in Go called Nexus.  It's the first
   bulletpoint on my resume.

   Nexus had severe stability and architectural issues I was
   brought on to fix.  The relationship with the contractors was strained, so code was the easy part!
   The rest was advocacy and building trust and consensus with the contractors, teaching, mentoring them, making sure all voices were heard, and making
   extra effort to invite them into the design of the new architecture when
   possible.

   So collaboration isn't a bolt-on for me, but a pretty fundamental part of how
   I work philosophically and practically.

   I'm an expert in Go, distributed systems, and API design throughout the
   full lifecycle (among many other things),
   who's been working on SaaS problems for 2U for the past nine years.
   I've worked with monitoring, observability, testing, CI/CD, PagerDuty.

   This job sounds spot on for me.
   I would love an opportunity to talk about it!
}
