%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Letter of Notice
% LaTeX Template
% Version 1.1 (21/11/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rashadul Islam (ross08@gmail.com) with modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % 11pt default font size, other options: 12pt and 10pt

\usepackage[a4paper, top=2cm]{geometry} % Use A4 paper size

\usepackage{xcolor} % Required for color customization

%\usepackage{fouriernc} % Use the New Century Schoolbook font, comment this line to use the default LaTeX font or replace it with another
\usepackage[sfdefault]{FiraSans} % Change this to use any font, but keep it simple

\definecolor{cvblue}{HTML}{304263} % Define a custom color for the heading box

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	DATE AND FROM ADDRESS
%----------------------------------------------------------------------------------------

\date{\vspace{1.5cm}\begin{flushleft}\today\end{flushleft}} % Use todays date and left-align it

\begin{letter}{\large \bfseries Unicorn} % From address or department

%----------------------------------------------------------------------------------------
%	HEADING BOX
%----------------------------------------------------------------------------------------

\colorbox{cvblue!90}{ % Creates a highlight behind the text using the previously-defined navy color

\parbox[t]{\linewidth}{ % Creates a box to take up the entire line width

\vspace*{14pt} % Whitespace above the text

\hfill \color{white} \textsc{\huge Senior Software Developer} % Right-aligned heading text

\vspace*{14pt} % Whitespace below the text
}}

%----------------------------------------------------------------------------------------
%	SIGNATURE
%----------------------------------------------------------------------------------------

\signature{
Jason Felice \\ % Your name
\small{E: jason.m.felice@gmail.com\\ M: +1-216-466-4122} % Contact information
}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Unicorn,}

{\bf TL;DR} I am a cross-stack, hands-on, top-tier engineer with significant EdTech
experience (as well as an actual human being and not a robot) and I'd love a chance to
consult with Unicorn.

For the last nine years, I've worked at 2U, Inc. -- the last few with Steven Weathers.
This comprised of three "jobs" in two different areas of the business.

The first was building a system for the standup of online degree programs, such as MBAs,
RNs, and a couple JDs.  It was a system of record about contract-related information, and
prompted and drove the manual and automated processes necessary to get new single-tenant
programs built.

The second was to whip the acquired bootcamps arm into shape, since they were not up to
company standards with regards to security or compliance, documentation, CI/CD, hosting,
monitoring or observability, and so forth.  Significant bits of code rearchitecting was
required to enable horizontal scaling and zero downtime deploys, as well as migrating
to using our internal OAuth system for access.

Here we maintained a SAML server implementation that was used by Canvas to authenticate
our users, several LTIs, some ETL processes, and much user provisioning code for things
like Zoom sessions.

The third role was back to the degrees side, working most heavily on a Salesforce data
caching system, but dealing with multiple microservices related to the enrollment
pipeline.

\closing{Sincerely,}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
