\def\company{Upstart}
\def\position{Senior Software Engineer, Home Lending}
\relevantskill{Java}{eriemobile,cronosysprojects,homepage,xpay}
\relevantskill{Kotlin+Other JVM}{centralpark,points}
\relevantskill{React}{centralpark,passport,nexus}
\relevantskill{SQL Databases}{passport,cronosysprojects,webtech}
\relevantskill{Cross-Team Projects}{nexus,homepage,xpay}
\relevantskill{Verbal + Written Comm.}{whitepaper,guided,centralpark}
\relevantskill{Challenging Authority}{whitepaper}
\def\coverbody{
   Hello!

   This job posting describes me!

   I've been a hands-on (read: coding) senior or principal engineer for 12 or more
   years, depending on how you count.  I spend most time coding, followed by mentoring and
   otherwise bringing up engineers, but I also step up to
   push for organizational change when necessary for the health of the tech
   team or greater org.  I hope my resume clearly communicates this part.

   Cross-team delivery has been necessary on many of my past projects.  Working
   to get face time from other teams who have their own priorities is a challenge
   for which I have a bag of tricks I've collected to minimize their disruption.
   If the friction is constant, especially for high-profile projects, it might
   imply organizational issues.

   I have written only a tiny bit of Kotlin in the past, but I also have 25 years or
   more of Java experience and experience on other JVM-based stacks, as well as a
   large bucket of other languages.  I'm competent
   with React.   I'm expert-level on PostgreSQL, MySQL, and SQL domain modeling.

   I'd love a chance to discuss this role!
}
